---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# glod

<!-- badges: start -->
[![R-CMD-check](https://github.com/mdsumner/glod/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdsumner/glod/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of glod is to plot the Geographer's Line of Death. 

## Installation

You can install the development version of glod like so:

``` r
pak::pak("mdsumner/glod")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(glod)
## basic example code
glod()

glod("+proj=laea +lat_0=90")
glod("+proj=laea +lat_0=-90")

## get just the data with plot = FALSE
str(glod("+proj=tmerc +lon_0=147", plot = FALSE))

## lots of fun!
glod("+proj=omerc +lonc=157 +lat_0=-42 +alpha=1")
```

## TODO

- stop those PROJ error messages ...
- put a radius on the extent so you can see more projections
- integrate with {bigcurve} so the line is just-dense-enough

## Code of Conduct
  
Please note that the glod project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
